Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-01-19 manuscript.tex

% describe initial and target states for this example
This numerical simulation demonstrates the ability of the proposed approach. 
We use multiple iterations of the reachability set to achieve a more complicated transfer.
In this manner, it is possible to design arbitrary transfers which are not possible using a single reachability computation.
Initially, it is assumed that the spacecraft lies on a circular geostationary orbit in the non-dimensional Earth-Moon three-body system. 
It is desired to transfer to a periodic orbit about the \( L_1 \) Lagrange point. 
The initial and target orbits are illustrated in~\cref{fig:geo_transfer_target}.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.5\textwidth]{initial_final} % requires the graphicx package
   \caption{Transfer target}
   \label{fig:geo_transfer_target}
\end{figure}
In order to effectively utilize the dynamics of the three-body system the stable manifold of the periodic orbit is targeted.
We seek to generate a transfer from the geostationary orbit onto the stable invariant manfiold.
Once on the manifold, the spacecraft will coast in an uncontrolled fashion and asymptotically arrive at the desired periodic orbit.

\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.5\textwidth]{third_reachability_set} % requires the graphicx package
   \caption{Reachable set after three iterations}
   \label{fig:third_reachability_set}
\end{figure}
We first generate the stable invariant manifold associated with the periodic orbit in order to determine our target set.
The stable manifold is propagated to the \Poincare section at \( y = 0 \), which is denoted by the horizontal black line in~\cref{fig:geo_transfer_full}.
Next, we compute the reachable sets originating on the geo-stationary orbit and subject to the maximum control constraint. 
The multiple shooting approach is used to solve the optimal control problem with two segments.
The initial geo-stationary orbit is used to initialize the interior point \( \vecbf{x}_i^{-} \).
We use the same initial guess of \( \vecbf{\lambda}_0\) as in~\cref{sec:periodic_orbit_transfer} and propogate over the fixed time horizon of the period of the geostationary orbit to initialize \( \vecbf{\lambda}_i^{-}\).

The first reachable set is computed beginning on the geostationary orbit at it's intersection with the \Poincare section and we again assume a upper bound on the thrust magnitude of \( u_{max} = 0.75 \).
The reachable set is generated by varying the angle \( \ang{0} \leq \theta < \ang{360} \) in~\cref{eq:constraints} defined on the \Poincare section.
This allows us to approximate the set of states that are achievable in the \( \parenth{x ,\dot{x}} \) space.
After each computation of the reachability set we pick a state which minimizes the distance on the \Poincare section towards the stable manifolds and is given as
\begin{align*}
	d(\vecbf{x}(N)) = \sqrt{\parenth{x - x_t}^2 + \parenth{\dot{x} - \dot{x}_t}^2}.
\end{align*}
From the reachable set, the trajectory which minimizes \( d \) is used to intialize the next reachability computation, or it will intersect the stable manifold region on the \Poincare section.
%A state is chosen from the reachable set which minimizes the distance on the \Poincare section to the stable manifold, illustrated in green in~\cref{fig:geo_transfer_poincare}, and is used as the initial condition for the next reachable set computation.
For example,~\cref{fig:third_reachability_set} shows the reachable set after three iterations in red and the minimum distance to the stable manifold in green.
The state and costate trajectories associated with this point on the rechable set is used to initialize the following iteration. 
In this manner, the multiple shooting algorithm solves the optimal control problem and generates reachable sets which move away from the intial orbit and towards the desired target.

>>>>

% describe initial and target states for this example
This numerical simulation demonstrates the ability of the proposed approach. 
We use multiple iterations of the reachability set to achieve a more complicated transfer.
In this manner, it is possible to design arbitrary transfers which are not possible using a single reachability computation.
Initially, it is assumed that the spacecraft lies on a circular geostationary orbit in the non-dimensional Earth-Moon three-body system. 
The geostationary orbit about the Earth is transformed into the rotating reference frame of the Earth-Moon three body problem.
In addition, we nondimensionalize the initial state to find \( \vecbf{x}_0 = \begin{bmatrix} 0.0972 & 0 & 0 & 3.0010\end{bmatrix}^T\) as the initial condition of the spacecraft on the geostationary orbit.
It is desired to transfer to a periodic orbit about the \( L_1 \) Lagrange point. 
The periodic orbit is defined by the initial condition \(\begin{bmatrix} 0.8057 & 0 & 0 & 0.2982 \end{bmatrix} \).
The initial and target orbits are illustrated in~\cref{fig:geo_transfer_target}.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.5\textwidth]{initial_final} % requires the graphicx package
   \caption{Transfer target}
   \label{fig:geo_transfer_target}
\end{figure}
In order to effectively utilize the dynamics of the three-body system the stable manifold of the periodic orbit is targeted.
We seek to generate a transfer from the geostationary orbit onto the stable invariant manfiold.
Once on the manifold, the spacecraft will coast in an uncontrolled fashion and asymptotically arrive at the desired periodic orbit.

\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.5\textwidth]{third_reachability_set} % requires the graphicx package
   \caption{Reachable set after three iterations}
   \label{fig:third_reachability_set}
\end{figure}
Next, we generate the stable invariant manifold associated with the periodic orbit in order to determine our target set.
The stable manifold is propagated to the \Poincare section at \( y = 0 \), which is denoted by the horizontal black line in~\cref{fig:geo_transfer_full}.
Next, we compute the reachable sets originating on the geo-stationary orbit and subject to the maximum control constraint. 
The multiple shooting approach is used to solve the optimal control problem with two segments.
For the first reachability set computation, the initial geostationary orbit is used to initialize the multiple shooting algorithm.
We use the same initial guess of \( \vecbf{\lambda}_0\) as in~\cref{sec:periodic_orbit_transfer} and propogate over the fixed time horizon of the period of the geostationary orbit to initialize \( \vecbf{\lambda}_i^{-}\).

The first reachable set is computed beginning on the geostationary orbit at it's intersection with the \Poincare section and we again assume a upper bound on the thrust magnitude of \( u_{max} = 0.75 \).
The reachable set is generated by varying the angle \( \ang{0} \leq \theta < \ang{360} \) in~\cref{eq:constraints} defined on the \Poincare section.
This allows us to approximate the set of states that are achievable in the \( \parenth{x ,\dot{x}} \) space.
After each computation of the reachability set we pick a state which minimizes the distance on the \Poincare section towards the stable manifolds as the function \( d \)
\begin{align*}
	d(\vecbf{x}(N)) = \sqrt{\parenth{x - x_t}^2 + \parenth{\dot{x} - \dot{x}_t}^2}.
\end{align*}
From the reachable set, the trajectory which minimizes \( d \) is used to intialize the next iteration.
Once the reachability set intersects the stable manifold, we can achieve a complete transfer from the initial geostationary orbit to the stable manifold of \( L_1 \).
%A state is chosen from the reachable set which minimizes the distance on the \Poincare section to the stable manifold, illustrated in green in~\cref{fig:geo_transfer_poincare}, and is used as the initial condition for the next reachable set computation.
For example,~\cref{fig:third_reachability_set} shows the reachable set after three iterations in red and the minimum distance to the stable manifold in green.
The state and costate trajectories associated with this point on the rechable set is used to initialize the following iteration. 
In this manner, the multiple shooting algorithm solves the optimal control problem and generates reachable sets which move away from the intial orbit and towards the desired target.
